%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} 

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mark Anderson} % Your name
\address{+1 660-864-5106 \\ admin@hatsu.dev \\ github.com/mcar43}  

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Bachelor of Science in Computer Science} \hfill {August 2015 - May 2020}
\\ 
Missouri University of Science \& Technology 
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages (5+ Years) & C++, Python, Java, C, HTML/CSS, Go, Bash, JS\\ 
    Industry Experience & Penetration Testing, Network Analysis, Software Engineering \\ & Security Orchestration and Automation, REST APIs, Scrum \\
    Tools & Metasploit, Kali Linux, Docker, Kubernetes, Swimlane, \\ & NPView, Maven, Make/CMake, Linux, Git \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
\begin{rSubsection}{1898 \& Co.}{August 2020 - Present}{Cybersecurity Analyst}{Kansas City, MO} 
    \item Custom implementation for Python SOAR and API 
    \item High level SIEM and SOAR design for a multi-millionare dollar project
    \item Firewall, Switch, and Router hardening and configuration analysis
    \item Windows HMI, PI Server, and Term Server hardening and configuration analysis
\end{rSubsection} 
%----------------------------------------------------------------------------------------
\begin{rSubsection}{CinemaCraft LLC}{November 2020 - Februrary 2021}{Senior Software Engineer}{}
\item Spearheaded development for assets that generated 102,710,516 unique views and \$150,000 in profit for the company.
    \item Interfaced with numerous libraries and APIs to compile and develop in an enterprise codebase.
    \item Managed multiple other departments to package up assets and resources into a final deliverable on a weekly deadline.
\end{rSubsection}

%----------------------------------------------------------------------------------------
\begin{rSubsection}{Burns \& McDonnell}{May 2019 - August 2020}{Cybersecurity Intern}{}
    \item Built networking infrastructure for a large scale Radiation Detection and Instant Alert System. 
    \item Facilitated processes and procedures for vulnerability assessments and network analysis. 
    \item Utilized popular security toolkits and software such as OpenVas, Nessus, and Vulnerator. 
\end{rSubsection}
%----------------------------------------------------------------------------------------
\begin{rSubsection}{National Informative Solutions Cooperative}{May 2018 - August 2018}{Software Engineering Intern}{}
    \item Automated the software engineering team's entire Quality Assurance workflow
    \item Developed quick turn around change requests for PL/SQL and COBOL applications
\end{rSubsection}
%----------------------------------------------------------------------------------------
\begin{rSubsection}{Parallel Computing Research Assistant}{May 2016 - August 2016}{Researcher}{}
    \item Simulated parallel computing using cellular automata for a high performance research team
    \item Designed highly optimized algorithms in CUDA
    \item Setup air gapped development environment and distributed machine images for secure development
\end{rSubsection}
\end{rSection} 

\begin{rSection}{Volunteer Experience}
\begin{rSubsection}{Microsoft TEALS}{August 2020 - Present} {Teacher} {} 
    \item Computer Science resource thats guided for underprivileged high school districts.
\end{rSubsection}

\end{rSection}

\end{document}
