%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} 

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mark Anderson} 
\address{+1 660-864-5106 \\ admin@hatsu.dev \\ github.com/mcar43}  

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Bachelor of Science in Computer Science} \hfill {August 2015 - May 2020}
\\ 
Missouri University of Science \& Technology 
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages & C++, Python, Java, C, HTML/CSS, Go, Bash, SQL\\ 
    Industry Experience & Penetration Testing, Network Analysis, Software Engineering, Encryption\\ & Security Orchestration and Automation, REST, Reverse Engineering\\
    Tools & Metasploit, Kali Linux, Docker, Kubernetes, Swimlane, \\ & NPView, Maven, Make/CMake, Valgrind, GDB, Ghidra \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
\begin{rSubsection}{1898 \& Co.}{August 2020 - Present}{Cybersecurity Analyst}{Kansas City, MO} 
    \item Assistend in design of a high availability Security Orchestration and Automation Solution.
    \item Implemented custom SOAR integrations using Python to interface with various security APIs.
    \item Conducted cybersecurity assessments for Operational Technology and Information Technology environments. 
\end{rSubsection} 
%----------------------------------------------------------------------------------------
\begin{rSubsection}{CinemaCraft LLC}{November 2020 - Februrary 2021}{Senior Software Engineer}{Remote}
    \item Spearheaded development for assets that generated !REPLACE! unique views and over \$150,000 in profit. 
    \item Developed in a large enterprise Java codebase utilizing various build automation tools for compilation.
    \item Managed multiple departments to package up assets and resources into a final deliverable on a weekly deadline.
\end{rSubsection}
%----------------------------------------------------------------------------------------
\begin{rSubsection}{Burns \& McDonnell}{May 2019 - August 2020}{Cybersecurity Intern}{Kansas City, MO}
    \item Assisted in the building of networking infrastructure for a large scale Radiation Detection and Instant Alert System. 
    \item Facilitated processes and procedures for vulnerability assessments and network analysis services. 
    \item Utilized popular security toolkits and software such as OpenVas, Nessus, and Vulnerator. 
\end{rSubsection}
%----------------------------------------------------------------------------------------
\begin{rSubsection}{National Informative Solutions Cooperative}{May 2018 - August 2018}{Software Engineering Intern}{Lake Saint Louis, MO}
    \item Automated and streamlined the majority of the Software Development team's quality assurance workflow.  
    \item Developed quick turn around customer change requests in PL/SQL, Cobol, and Java applications.
    \item Managed an enterprise database of production records in Oracle Database and Oracle Cloud Infrastructure. 
\end{rSubsection}
%----------------------------------------------------------------------------------------
\begin{rSubsection}{Parallel Computing Research Assistant}{May 2016 - August 2016}{Researcher}{Rolla, MO}
    \item Simulated parallel proceeses for a one-dimensional rule-based cellular automata non-qubit quantum adder 
    \item Developed multithreaded algorithms in CUDA and C++ for parallel simulation. 
    \item Setup an air gapped development environment and distributed machine images for secure development
\end{rSubsection}
\end{rSection} 

\begin{rSection}{Volunteer Experience}
\begin{rSubsection}{Microsoft TEALS}{August 2020 - Present} {Teaching Assistant} {Remote} 
    \item Computer Science professional resource for teaching assistance in underprivileged high school districts.
\end{rSubsection}
\end{rSection}
\clearpage

\begin{rSection}{Project Experience}
    \begin{rSubsection}{Library Analytics System (LiSpy)}{}{\textbf{Tech Used:} TShark, Linux, REST, ExpressJS, Bash}{} 
        \item Dispersed Raspberry Pi's listening for mobile probe requests to estimate a live population density map of the Missouri S\&T library. 
        \item Built and maintained linux image which allowed for plug and collect deployment of Raspberry Pi sensors.
        \item Probe request RSSI values were used to accurately triangulate location of requests inside the library within a 5 foot margin of error. 
    \end{rSubsection}

    \begin{rSubsection}{PDGA Calculator}{}{\textbf{Tech Used:} Beautiful Soup, SQLAlchemy, Python, Flask, sqlite}{} 
        \item Built a full-stack web app that scrapes the PDGA website for player round ratings, builds a database, and allows users to edit and add round ratings to calculate a future rating.
        \item Implemented a polite rate limited webscraper with dynamic request intervals based on server response times to minimize scraping load to PDGA server.
        \item Optimized the scraping process by implementing hash checks against player numbers to see if additional scraping is required.
    \end{rSubsection}

    \begin{rSubsection}{Challonge C++ API Bindings}{}{\textbf{Tech Used:} C++, cURL, JSON, cmake}{} 
        \item Allowed the simple usage of the Challonge Tournament API using C++ for the Missouri S\&T Smash Club to create custom bracket applications.
        \item Developed multiple wrapper classes for various API objects to streamline API usage and implement object oriented principles to the API. 
        \item Added various utility functions that add additional functionality to expand on the base API. 
    \end{rSubsection}
\end{rSection}
\end{document}
